Examining readability of text generated through GPT-3

### 2023-03-31 paper/paper.tex
finalize paper

\begin{document}
\maketitle
\begin{abstract}
    This paper examines readability-related metrics of AI-generated text, specifically texts produced by OpenAI's GPT-3. Generation was performed for the English language across 10 topics and the 6 proficiency levels defined by the CEFR framework, and outputs were compared with Simple Wikipedia and (standard) Wikipedia articles on the same topics. 7 commonly used complexity metrics have been employed, targeting chiefly lexis and syntax. In the limited scope of this experiment, GPT-3 is observed to at least partially aware of what constitutes reading difficulty.
\end{abstract}

@@

The feautre "Words in Top 3000 English words" uses unigram frequencies from the Google Web Trillion Word corpus\footnote{\url{https://ai.googleblog.com/2006/08/all-our-n-gram-are-belong-to-you.html}} to isolate the 3000 most frequent words of the English language. Many research approaches to readability employ similar ideas to gain insight into the lexical complexity of texts, such as the BIV (basic Italian vocabulary) employed by \citep{dellorletta-etal-2011-read}.

@@

Interesting discussions can be had around topics as well, since, depending on GPT-3's ability to generalize across domains, certain areas might be problem areas for it. For example, "semantics" and "quantum mechanics" would be hard to write about for A1 level students as they are likely to be children who have not interacted with those fields yet.

@@

This work attempted to gauge true readability levels of GPT-3 output texts with prompts across 10 topics and CEFR proficiency levels, optimising thus for the second language learning application environment. Outputs computed from the metrics set suggest that GPT-3 is at least somewhat aware of syntax and lexis when performin generation for a target readability level.

>>>>

\begin{document}
\maketitle
\begin{abstract}
    This paper examines readability-related metrics of AI-generated text, specifically texts produced by OpenAI's GPT-3. Generation was performed for the English language across 10 topics and the 6 proficiency levels defined by the CEFR framework, and outputs were compared with Simple Wikipedia and (standard) Wikipedia articles on the same topics. 7 commonly used complexity metrics have been employed, targeting chiefly lexis and syntax. In the limited scope of this experiment, GPT-3 is observed to be at least partially aware of what constitutes reading difficulty.
\end{abstract}

@@

The feature "Words in Top 3000 English words" uses unigram frequencies from the Google Web Trillion Word corpus\footnote{\url{https://ai.googleblog.com/2006/08/all-our-n-gram-are-belong-to-you.html}} to isolate the 3000 most frequent words of the English language. Many research approaches to readability employ similar ideas to gain insight into the lexical complexity of texts, such as the BIV (basic Italian vocabulary) employed by \citep{dellorletta-etal-2011-read}.

@@

Interesting discussions can be had around topics as well, since, depending on GPT-3's ability to generalize across domains, certain areas might constitute problem for it. For example, "semantics" and "quantum mechanics" would be hard to write about for A1 level students as they are likely to be children who have not interacted with those fields yet.

@@

This work attempted to gauge true readability levels of GPT-3 output texts with prompts across 10 topics and CEFR proficiency levels, optimising for the second language learning application environment. Outputs computed from the metric set suggest that GPT-3 is at least somewhat aware of syntax and lexis when performin generation for a target readability level.
